Figures

### 2021-10-20 manuscript/figures.Rmd
towards submission

```{r 01_iris, fig.cap="Sepal length versus width", echo=FALSE, fig.width=1,out.height="4in"}
knitr::include_graphics("../figures/01_iris-1.pdf")
```

>>>>

```{r fig.cap="Realization of a Pareto (A) probability density function and (B) complementary cumulative distribution
function.", echo=FALSE, fig.width=1,out.height="4in"}
knitr::include_graphics("manuscript/figures/pareto_demo-1.pdf")
```
